---
title: 'WGSmapp Vignette'
author: "Rujin Wang, Danyu Lin, Yuchao Jiang"
date: "`r format(Sys.Date())`"
output:
  html_document:
    highlight: pygments
    toc: true
---
# Mappability
This package provides whole-genome mappability tracks on human hg19/hg38 assembly. We employed the 100-mers mappability track from the ENCODE Project and computed weighted average of the mappability scores if multiple ENCODE regions overlap with the same bin.
```{r, message=FALSE}
library(WGSmapp)
data("mapp_hg19")
mapp_hg19
```


# Blacklist regions
“Blacklist” bins, including [segmental duplication regions](http://humanparalogy.gs.washington.edu/build37/data/GRCh37GenomicSuperDup.tab) and [gaps in reference assembly](https://gist.github.com/leipzig/6123703) from telomere, centromere, and/or heterochromatin regions are included.

```{r}
library(WGSmapp)
# Get segmental duplication regions
seg.dup = read.table(system.file("extdata", "GRCh37GenomicSuperDup.tab", package = "WGSmapp"), head = TRUE)
# Get hg19 gaps
gaps = read.table(system.file("extdata", "hg19gaps.txt", package = "WGSmapp"), head = TRUE)

head(seg.dup)
head(gaps)
```


# BAM files
The dataset consists of three assembled .bam files of single-cell whole genome sequencing from 10X Genomics Single-Cell CNV solution for illustration purposes. These three cells are from section E of five adjacent tumor dissections of a breast cancer patient. Corresponding cellular barcode tags are "AAAGCAATCTGACGCG", "GCAGTTACACTGTATG", and "CTCGTCACAGGTTAAA".

